\chapter{Introduction}\label{cha:introduction}

Understanding nature's weakest fundamental force - gravity - has been a persistent challenge ever since Newton formulated the laws of gravitational force in 1687 \cite{Newton_1687}.
Newton's equations were groundbreaking, providing unprecedented accuracy in predicting planetary motion and establishing mathematics as the universal language of physical description.
In 1774, Maskelyne conducted the first measurement of gravitational attraction between objects other than astronomical bodies, solidifying the concept of the interaction of masses across multiple orders of magnitude \cite{Maskelyne_1775,Davies_1985}. 
Cavendish measured the gravitational constant $G$ using a torsion pendulum in 1798, providing the first quantitative determination of the weak gravitational coupling \cite{Cavendish_1798}.
Einstein revolutionized our understanding of gravity with his theory of general relativity, offering a geometric interpretation of spacetime \cite{Einstein_1916}. Yet, the fundamental nature of gravity remains elusive. Whether gravity is purely classical or fundamentally quantum is one of the most pressing and debated questions in modern physics and many different theories for unifying general relativity and quantum mechanics have emerged \cite{Becker_2007, Ashtekar_1986, Oppenheim_2023}.
The extraordinary success of quantum field theory for electromagnetic, weak, and strong interactions suggests that gravity may also have a quantum foundation.

Building on Feynman's ideas from 1957 \cite{Rickles_2011,Zeh_2011}, several subsequent works \cite{Lindner_2005,Kafri_2013,Schmoele_2016,Krisnanda_2017} have proposed searching for gravitationally induced entanglement as a key signature of the quantum nature of gravity that would experimentally establish the necessity for a new theory of gravity.
Advances in quantum optomechanics have led to several recent experimental proposals \cite{Bose_2017,Marletto_2017,Krisnanda_2020}, that outline concrete roadmaps for conducting such experiments e.g. with levitated nanoparticles.
In \cref{cha:first-look} of this thesis, the arguments and assumptions behind these proposals are discussed and the general experimental setup is explained. A useful framework of later employed methods is outlined.
The necessity of a Faraday shield in the experiments is explained as well as potential occurring issues due to Casimir interactions \cite{Casimir_1948} between the introduced shield and the particles.
\Cref{cha:casimir-effect} introduces the Casimir force and establishes approximation models for short- and long-range interactions. The effect of rough and uneven surfaces is studied.

The decoherence effect and the consequent loss of entanglement caused by stochastic variations in the experimental initialization are analyzed in-depth in \cref{cha:entanglement-generation}. Potential modifications in the setup and the proposed parameter-space as well as the ability to trap and levitate the particles close to the shield is discussed. 
\Cref{cha:the-shield} estimates the required size and thickness of the Faraday shield to sufficiently suppress unwanted interactions between the masses. Additionally, effects of thermal vibrations of the shield on entanglement generation are calculated and analyzed.